{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
More introduction.

@@

\subsection{What is Required of Users} %%%
\indent \indent For users to circumvent censorship in their resident countries, they will need to 
configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
have been blocked by the government. There is a configuration wizard to help guide users through setting up their connection, but they require the user to provide IP addresses of proxies or bridges to use.

@@

\section{UX sprint}  %%%%
\indent \indent {\color {red} Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story.

Appendix ~\ref{sec:pilot}. }

It is easy to overestimate user comprehension and therefore be 
misguided for user behavior. Even though people download and install things all the time, 
they do not know how to do it securely, and worse, they are habituated into doing it in the 
insecure manner. Of course, this is because the average user's objective is not security. 
For instance, most of our participants thought the download source was a legitimate site because
of the look and feel of the site and none our our participants thought to verify the download, 
even though there were clear instructions to do so on the download page.

During this pilot, the users were struggling with confusing bugs, such as flash errors which
say ``Firefox'' rather than ``Tor,'' disappearing buttons on the configuration window, and errors when
launching Tor from the download dialog rather than from their applications folder. This resulted in our 
participants spending most of their time on the download and install tasks, rather than 
navigating a robust menu or questioning the clarity of provided security guarantees.

@@

\subsection{Takeaways} 
\indent \indent During the pilot study, we were attempting to test out a comprehensive set of 
features for the Tor Browser. Our users had difficulties completing all the given tasks in the 
time alloted for the experiment. Additionally, user fatigue was very evident, with users not 
engaging in the later set of tasks after being tired from the download and install process. 
To ensure that the experiment does not cause user fatigue, we select a smaller set of features 
as the target for the full-scale study.  After deliberating with Tor developers, and testing out
various features on our own, we chose to focus on the Tor Browser connection configuration 
dialog because of its crucial role in censorship circumvention.

@@

\section{Related Work} %%%
%%%Tor
 {\color {red} The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
And that is pretty much it for Tor usability stuff.} %find more if it exists

@@

%%%User behavior
\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.}

%%% Other Usability stuff 
\indent \indent {\color {red}  cite work which has made a huge impact on how people use it, and 
other things which still remain broken because of usability issues.}

@@

@@

Our online artifacts of our completed pilot study, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
\end{itemize}

>>>>

The heart of our investigation will be a large-scale user study
that measures how effectively users are able to complete
basic web browsing tasks in the presence of a censor.
We will place users in a controlled network environment
that simulates the kind of censorship conditions that many
users around the world face daily.
We will be testing specific circumvention software---namely,
Tor Browser---though our larger contribution is to establish
a usability testing methodology for the evaluation
of this kind of software.

@@

\subsection{What is Required of Users}
\indent \indent For users to circumvent censorship in their resident countries, they will need to 
configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
have been blocked by the government. There is a configuration wizard to help guide users through setting up their connection, but they require the user to provide IP addresses of proxies or bridges to use.

@@

\section{A Pilot Tor Usability Study} 
\indent \indent We ran a pilot Tor usability study to test the usability of Tor as an anonymity tool,
targeting a specific demographic of users known to use Tor (journalists who have reported in other
countries) and aiming to identify how well they could understand Tor's non-typical behaviors and 
navigate advanced settings. For the full details of this pilot experiment, we refer you to Appendix ~\ref{sec:pilot}.

During this pilot, the users were struggling with confusing bugs, such as flash errors which
say ``Firefox'' rather than ``Tor,'' disappearing buttons on the configuration window, and errors when
launching Tor from the download dialog rather than from their applications folder. This resulted in our 
participants spending most of their time on the download and install tasks, rather than 
our original task for navigating a robust menu or questioning the clarity of provided security 
guarantees. We took the opportunity to collaborate with Tor developers to make changes for the Tor 
Browser and use the lessons learned to design our large-scale user study on testing Tor as a 
censorship circumvention tool.

@@

\subsection{Lessons Learned} 
\indent \indent During the pilot study, we were attempting to test out a comprehensive set of 
features for the Tor Browser. Our users had difficulties completing all the given tasks in the 
time alloted for the experiment. Additionally, user fatigue was very evident, with users not 
engaging in the later set of tasks after being tired from the download and install process. 
To ensure that the experiment does not cause user fatigue, we select a smaller set of features 
as the target for the full-scale study.  After deliberating with Tor developers, and testing out
various features on our own, we chose to focus on the Tor Browser connection configuration 
dialog because of its crucial role in censorship circumvention.

@@

\section{Related Work} %%%

\subsection{Usability work on Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to great usability improvements ~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective. Researchers provide guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction. Key takeaways from this work includes 
finding out that exposure to how Tor works may be difficult for users to understand, and that 
familiar, non-technical language is critical for communication. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

This will be the first experiment to evaluate Tor's usability as a censorship circumvention tool.
Previous work on evaluating the usability of Tor as an anonymity system have been fruitful. 
Norcie \etal identified ``stop points,'' or barriers to installing and using Tor to help streamline
the interface. Key stop points included the ability to discriminate between anonymized and non-
anonymized browser windows while using tor, unclear download and install processes, and 
confusion as to why the Tor behaves in peculiar ways ~\cite{norcie2012eliminating}. A follow up
study by Norcie \etal verifies that the changes recommended to the Tor Project were indeed 
effective at reducing stopping points mentioned in the previous work. The authors also present
design heuristics for designing usable anonymous systems, such as easy installation, communicating
tradeoffs made to users, and informing why, not how, precautions are taken for security guarantees ~\cite{norcie2014johnny}.

\subsection{Usable Security and User Behavior}
\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.}

@@

@@

%It is easy to overestimate user comprehension and therefore be 
%misguided for user behavior. During this process, we discovered why 
%previous studies had not concentrated on a specific user 
%demographic or focus on advanced features. 
%Even though people download and install on a frequent basis, 
%they do not know how to do it securely and are habituated into doing it in the 
%insecure manner. Of course, this is because the average user's objective is not security. 
%For instance, most of our participants thought the download source was a legitimate site because
%of the look and feel of the site and none our our participants thought to verify the download, 
%even though there were clear instructions to do so on the download page.

@@

\indent \indent  Our online artifacts of our completed pilot study, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
\end{itemize}
